Beyond ``Horizontal'' and ``Vertical'':\\ The Welfare Effects of Complex Integration\tnoteref{t1}

### 2024-08-09 doc/VerticalArrangements.tex
added back in TrashSimsCompareAll.png/ Other minor nits.
modified picutres per Gloria's 8/6 comments

@@

\begin{figure}
\centering
\caption{The sensitivity of the Republic/Santek simulation results to changes in the bargaining power parameter. `All' changes the bargaining power paramtere for all non-vertically integrated firms. `Santek:Republic' changes the bargaining power parameter for just the Santek/Republic product. `WasteConn:Republic' changes the bargaining power parameter for just the WasteConn:Republic product. The Dashed line displays baseline results.}
\includegraphics{output/trashbarg.png}\\
\footnotesize{Notes: ``WasteConn'' stands for Waste Connections.}
\label{fig:TrashBarg}
\end{figure}

\begin{figure}
\centering
\caption{The sensitivity of the Republic/Santek simulation results to changes in the outside share. The absolute value of the market elasticity corresponding to the change in ouside share is in parentheses. Baseline results assume 0 outside share.}
\includegraphics{output/trashelast.png}\\
\footnotesize{Notes: ``WasteConn'' stands for Waste Connections.}
\label{fig:TrashElast}
\end{figure}

\begin{figure}
\centering
\caption{The sensitivity of the Republic/Santek simulation results to changes in the nesting parameter.`Integrated' assumes that all vertically integrated products are in a single nest, while `Landfill` assumes that all collectors that use the same landfill are in a single nest. A nesting parameter of 0 displays baseline results. }
\includegraphics{output/trashnest.png}\\
\footnotesize{Notes: ``WasteConn'' stands for Waste Connections.}
\label{fig:TrashNest}
\end{figure}

>>>>

\begin{figure}
\centering
\caption{Republic/Santek Simulations: Full vs. Partial Models}
\includegraphics[scale=1.0]{output/TrashSimsCompareAll.png}\\
\footnotesize{Notes: ``WasteConn'' stands for Waste Connections.}
\label{fig:TrashSimsFirms}
\end{figure}

@@

\begin{figure}
\centering
\caption{The sensitivity of consumer welfare in Santek/Republic merger simulations to changes in the bargaining power parameter.
%`All' changes the bargaining power paramtere for all non-vertically integrated firms. `Santek:Republic' changes the bargaining power parameter for just the Santek/Republic product. `WasteConn:Republic' changes the bargaining power parameter for just the WasteConn:Republic product. The Dashed line displays baseline results.
}
\includegraphics{output/trashbarg.png}\\
\footnotesize{Notes: ``WasteConn'' stands for Waste Connections.}
\label{fig:TrashBarg}
\end{figure}

\begin{figure}
\centering
\caption{The sensitivity of consumer welfare in the Republic/Santek simulations to changes in the outside share. The absolute value of the market elasticity corresponding to the change in outside share is in parentheses. Baseline results assume 0 outside share.}
\includegraphics{output/trashelast.png}\\
\footnotesize{Notes: ``WasteConn'' stands for Waste Connections.}
\label{fig:TrashElast}
\end{figure}

\begin{figure}
\centering
\caption{The sensitivity of consumer welfare in the Republic/Santek simulations to changes in the nesting parameter.`Integrated' assumes that all vertically integrated products are in a single nest, while `Landfill` assumes that all collectors that use the same landfill are in a single nest. A nesting parameter of 0 displays baseline results. }
\includegraphics{output/trashnest.png}\\
\footnotesize{Notes: ``WasteConn'' stands for Waste Connections.}
\label{fig:TrashNest}
\end{figure}
